\documentclass[11pt, a4paper, twoside]{report}
%\usepackage[a4paper, portrait, margin=1in]{geometry}

\usepackage{import}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{multirow}

\usepackage{fontspec}
\usepackage{unicode-math}

\usepackage[
    style=authoryear-icomp,
    citestyle=authoryear-icomp
]{biblatex}
\addbibresource{thesis.bib}
\addbibresource{Iris-Information-Obfuscation/references.bib}

\DeclareLabeldate[online]{%
  \field{date}
  \field{year}
  \field{eventdate}
  \field{origdate}
  \field{urldate}
}

\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{csquotes}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[toc, acronym]{glossaries}
\usepackage{nomencl}

\usepackage{todonotes}

\usepackage{quotchap}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{wrapfig}
\pgfplotsset{compat=1.16}
\usetikzlibrary{shapes.geometric, arrows}

\usepackage{booktabs}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[LE]{}
\fancyhead[RO]{}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\include{diagram-config}


\include{glossary}



\title{Obfuscation of sensitive information in eye information processes}
\author{Anton Mølbjerg Eskildsen (aesk@itu.dk)\\\small{STADS: KISPECI1SE}}
\date{November 2020}

\begin{document}
\setmathfont{STIX2Math}[
Extension={.otf},
Path=./fonts/,
Scale=1]
\setmainfont{STIX2Text}[
Extension={.otf},
Path=./fonts/,
UprightFont={*-Regular},
BoldFont={*-Bold},
ItalicFont={*-Italic},
BoldItalicFont={*-BoldItalic}]

\maketitle

\abstract{In this thesis, I present an initial proposal for modelling sensitive information in eye-tracking and defining methods for selective information removal. A communication-based, probabilistic model is proposed for eye information processes (EIP). The model frames obfuscation as a diverging optimisation of signal uncertainty, where the goal is to selectively decrease mutual information and increase conditional entropy of signals encoded by eye properties. The model is used in an analysis of existing and new methods for obfuscating iris patterns. I perform a stochastic grid-search of the proposed methods parameter spaces to select optimal settings given different gaze accuracy constraints. A second experiment estimates precise metrics for iris recognition performance and gaze accuracy for the selected parameter values. The new approaches outperform existing ones and do so as predicted by the proposed EIP model. The proposed information-based measure of obfuscation level is supported by a correlation of $0.91$ between it and a measure derived from an iris recognition algorithm. I discuss the results in relation to the general problem of removing information from eye-tracking data and present the details of the software systems developed for the experiments and analysis.}

\tableofcontents

\newpage
\begin{center}
\vspace*{\stretch{1}}
\emph{This thesis was written as a final part of the master of science in computer science programme at the IT University of Copenhagen. It represents my own original work and any uses of external resources, whether they be technical or literary, have clearly been marked as such.}
\vspace*{\stretch{1}}
\end{center}
\newpage

\include{chapters/introduction}
\include{chapters/background}
\include{chapters/theory}
\include{chapters/infosignal}


\include{article}

\include{chapters/method}

\include{chapters/results}

\include{chapters/learning}

\include{chapters/conclusion}

\printbibliography

\newpage

%\printnoidxglossaries
%\printnomenclature[1in]

\newpage
\include{appendix}

\end{document}
